---
title: "pallas"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{pallas}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r knitr-options, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# 🦉 pallas: An R package to compose and query SPARQL. 

## Introduction
The `pallas` package allows users to query SPARQL endpoints from R. As composing
SPARQL queries can be complicated, `pallas` also provides a set of utilities in 
the S7 framework to assist the user. 

## Installation instructions

Get the latest stable `R` release from [CRAN](http://cran.r-project.org/). Then
install `pallas` from [GitHub](https://github.com/minotau-R/pallas) 
with `remotes`: 

```{r, 'remotes-install', eval = FALSE}
install.packages("remotes")
remotes::install_github("minotau-R/pallas")
```


```{r setup}
library(pallas)
```

We can use `map_endpoint()` to take information about what SPARQL terms, namely 
classes and predicates, are defined at a given endpoint. `map_endpoint()` takes 
the URL of an endpoint as input and returns an object of the `OWL` S7 class.

```{r map-endpoint, cache = TRUE}
endpoint_url = "https://sparql.uniprot.org/"
x <- map_endpoint(endpoint_url)
```

`OWL` objects contain [Web Ontology Language](https://www.w3.org/OWL/) (OWL). A 
typical SPARQL query consists of at least three parts: 

1. prefix declarations
2. query type (SELECT, ASK, CONSTRUCT, DESCRIBE) and arguments
3. WHERE clause
This is also reflected in the `OWL` class: 

```{r show-OWL}
x
```

Printing the object will show our SPARQL code so far. It will also give some 
remarks regarding the SPARQL code we want to write. We can specify where-clauses
using the function `where_clause()`:

```{r where-clause}
x |>
    where_clause(C.Enzyme(?a)) |>
    where_clause(P.alternativeName(g:h ~ ?j)) |>
    where_clause(P.activity(?d ~ e:f),
                 C.Cluster(b:c))
```

```{r query-demo, cache=TRUE}
res <- x |> 
  select_query("SELECT ?protein") |>
  where_clause(
    C.Protein(?protein),
    triple("?protein", "core:mnemonic", "'A4_HUMAN'")
    ) |> 
  as.SPARQL() |>
  send_query(endpoint_url = "https://sparql.uniprot.org/")

res

```

